---
title: "Plots & Tables: All methods"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(kableExtra)

# Load design matrix
miss.conditions = readRDS("/Users/zinobrystowski/Desktop/Desktop/Leiden/LU Master/Internship/Design Matrix Revision/miss.conditions.rds")

# Load results for each method

meta_mean = readRDS("/Users/zinobrystowski/Desktop/Desktop/Leiden/LU Master/Internship/Results/Outcome measures/Meta mean/meta_mean_outcome")

meta_cv = readRDS("/Users/zinobrystowski/Desktop/Desktop/Leiden/LU Master/Internship/Results/Outcome measures/Meta CV/meta_cv_outcome")

meta_pmm = readRDS("/Users/zinobrystowski/Desktop/Desktop/Leiden/LU Master/Internship/Results/Outcome measures/Meta PMM/meta_pmm_outcome")

meta_forest = readRDS("/Users/zinobrystowski/Desktop/Desktop/Leiden/LU Master/Internship/Results/Outcome measures/Meta forest/meta_forest_outcome")

CCA = readRDS("/Users/zinobrystowski/Desktop/Desktop/Leiden/LU Master/Internship/Results/Outcome measures/CCA/CCA_outcome")

CDA = readRDS("/Users/zinobrystowski/Desktop/Desktop/Leiden/LU Master/Internship/Results/Outcome measures/CDA/CDA_outcome")
```


```{r, echo=F}
### Indeces assignment by a) number of views and b) view(s) with missing data

one_view_one = c(1:100, 401:500)
one_view_two = c(101:200, 501:600)
one_view_three = c(201:300, 601:700)
one_view_four = c(301:400, 701:800)

two_views_one_two = c(801:900, 1401:1500, 2001:2100, 2601:2700)
two_views_one_three = ( two_views_one_two + 100 )
two_views_one_four = ( two_views_one_three + 100 )
two_views_two_three = ( two_views_one_four + 100 )
two_views_two_four = ( two_views_two_three + 100 )
two_views_three_four = ( two_views_two_four + 100 )

```


### Test Accuracy 


```{r, echo = F} 

# Create 100 x 80 matrices for each method

# Create an object with the names of objects containing the results of each method
methods = c("meta_mean", "meta_cv", "meta_pmm", "meta_forest", "CCA", "CDA")

# Create two list objects, one to collect matrices and one to collect means and SDs
matrices = list()
Means_SDs = list()

# Create a second index j to update with each iteration
j = 1

for (i in methods) {
  
  # Create and save accuracy scores as matrix where each condition appears as a column
  matrices[[j]] = matrix( get( paste0(i) )$TestAccuracy, ncol = 80)
  
  # Use matrices to create a table with mean and SD for each method
  Means_SDs[[j]] = data.frame( mean = apply( matrices[[j]] , 2, mean),
                               sd = apply( matrices[[j]] , 2, sd))
  
  # Assign names
  names(matrices) [[j]] = paste0("mat_",i)
  
  names(Means_SDs) [[j]] = paste0("TA_table_", i)
  
  # Update second index j
  j = j + 1 
  
}
  
```

#### Number of views = 1

```{r, echo = F}

# Create a matrix to collect values for the later table
table = matrix(0, nrow = 4, ncol = 6)

# object containing objects with indeces for each level of missingness in views
views = c( "one_view_one", 
           "one_view_two", 
           "one_view_three", 
           "one_view_four" )

for ( i in 1:6){  # columns
  
  for ( j in 1:4 ){ # rows
    
        table[j,i] = mean ( matrices[[i]] [ get( views[j] ) ] )
                           
    }
} 

# Transform to data frame and assign col- and row names
table = as.data.frame(table)
colnames(table) = methods
rownames(table) = c(1:4)

# Print object as table        
table %>%   
  kbl(caption = "Test Accuracy: Size of views and Signal / Noise differentiation for Nviews = 1", digits = 2, row.names = TRUE) %>%
  kable_classic( full_width = T, html_font = "Times New Roman", position = "left")

```


#### Number of views = 2


```{r, echo = F}

# Create a matrix to collect values for the later table
table = matrix(0, nrow = 6, ncol = 6)

# object containing objects with indeces for each level of missingness in views
views = c(
  "two_views_one_two",
  "two_views_one_three",
  "two_views_one_four",
  "two_views_two_three",
  "two_views_two_four",
  "two_views_three_four"
)
  

for ( i in 1:6){  # columns
  
  for ( j in 1:6 ){ # rows
    
        table[j,i] = mean ( matrices[[i]] [ get( views[j] ) ] )
                           
    }
} 

# Transform to data frame and assign col- and row names
table = as.data.frame(table)
colnames(table) = methods
rownames(table) = views

# Print object as table        
table %>%   
  kbl(caption = "Test Accuracy: Size of views and Signal / Noise differentiation for Nviews = 2", digits = 2, row.names = TRUE) %>%
  kable_classic( full_width = T, html_font = "Times New Roman", position = "left")

```


### Mean Squared Error of Probabilities (MSEP)

```{r, echo = F}

# Create 100 x 80 matrices for each method

# Create an object with the names of objects containing the results of each method
methods = c("meta_mean", "meta_cv", "meta_pmm", "meta_forest", "CCA", "CDA")

# Create two list objects, one to collect matrices and one to collect means and SDs
matrices = list()
Means_SDs = list()

# Create a second index j to update with each iteration
j = 1

for (i in methods) {
  
  # Create and save accuracy scores as matrix where each condition appears as a column
  matrices[[j]] = matrix( get( paste0(i) )$MSEP, ncol = 80)
  
  # Use matrices to create a table with mean and SD for each method
  Means_SDs[[j]] = data.frame( mean = apply( matrices[[j]] , 2, mean),
                               sd = apply( matrices[[j]] , 2, sd))
  
  # Assign names
  names(matrices) [[j]] = paste0("mat_",i)
  
  names(Means_SDs) [[j]] = paste0("TA_table_", i)
  
  # Update second index j
  j = j + 1 
  
}
  
```

#### Number of views = 1

```{r, echo = F}

# Create a matrix to collect values for the later table
table = matrix(0, nrow = 4, ncol = 6)

# object containing objects with indeces for each level of missingness in views
views = c( "one_view_one", 
           "one_view_two", 
           "one_view_three", 
           "one_view_four" )

for ( i in 1:6){  # columns
  
  for ( j in 1:4 ){ # rows
    
        table[j,i] = mean ( matrices[[i]] [ get( views[j] ) ] )
                           
    }
} 

# Transform to data frame and assign col- and row names
table = as.data.frame(table)
colnames(table) = methods
rownames(table) = c(1:4)

# Print object as table        
table %>%   
  kbl(caption = "MSEP: Size of views and Signal / Noise differentiation for Nviews = 1", digits = 2, row.names = TRUE) %>%
  kable_classic( full_width = T, html_font = "Times New Roman", position = "left")

```


#### Number of views = 2


```{r, echo = F}

# Create a matrix to collect values for the later table
table = matrix(0, nrow = 6, ncol = 6)

# object containing objects with indeces for each level of missingness in views
views = c(
  "two_views_one_two",
  "two_views_one_three",
  "two_views_one_four",
  "two_views_two_three",
  "two_views_two_four",
  "two_views_three_four"
)
  

for ( i in 1:6){  # columns
  
  for ( j in 1:6 ){ # rows
    
        table[j,i] = mean ( matrices[[i]] [ get( views[j] ) ] )
                           
    }
} 

# Transform to data frame and assign col- and row names
table = as.data.frame(table)
colnames(table) = methods
rownames(table) = views

# Print object as table        
table %>%   
  kbl(caption = "MSEP: Size of views and Signal / Noise differentiation for Nviews = 2", digits = 2, row.names = TRUE) %>%
  kable_classic( full_width = T, html_font = "Times New Roman", position = "left")

```



### Mean proportion of correctly selected views (MPsV)

```{r, echo = F}

# Create 100 x 80 matrices for each method

# Create an object with the names of objects containing the results of each method
methods = c("meta_mean", "meta_cv", "meta_pmm", "meta_forest", "CCA", "CDA")

# Create two list objects, one to collect matrices and one to collect means and SDs
matrices = list()
Means_SDs = list()

# Create a second index j to update with each iteration
j = 1

for (i in methods) {
  
  # Create and save accuracy scores as matrix where each condition appears as a column
  matrices[[j]] = matrix( get( paste0(i) )$MPsV, ncol = 80)
  
  # Use matrices to create a table with mean and SD for each method
  Means_SDs[[j]] = data.frame( mean = apply( matrices[[j]] , 2, mean),
                               sd = apply( matrices[[j]] , 2, sd))
  
  # Assign names
  names(matrices) [[j]] = paste0("mat_",i)
  
  names(Means_SDs) [[j]] = paste0("TA_table_", i)
  
  # Update second index j
  j = j + 1 
  
}
  
```

#### Number of views = 1

```{r, echo = F}

# Create a matrix to collect values for the later table
table = matrix(0, nrow = 4, ncol = 6)

# object containing objects with indeces for each level of missingness in views
views = c( "one_view_one", 
           "one_view_two", 
           "one_view_three", 
           "one_view_four" )

for ( i in 1:6){  # columns
  
  for ( j in 1:4 ){ # rows
    
        table[j,i] = mean ( matrices[[i]] [ get( views[j] ) ] )
                           
    }
} 

# Transform to data frame and assign col- and row names
table = as.data.frame(table)
colnames(table) = methods
rownames(table) = c(1:4)

# Print object as table        
table %>%   
  kbl(caption = "MPsV: Size of views and Signal / Noise differentiation for Nviews = 1", digits = 2, row.names = TRUE) %>%
  kable_classic( full_width = T, html_font = "Times New Roman", position = "left")

```


#### Number of views = 2


```{r, echo = F}

# Create a matrix to collect values for the later table
table = matrix(0, nrow = 6, ncol = 6)

# object containing objects with indeces for each level of missingness in views
views = c(
  "two_views_one_two",
  "two_views_one_three",
  "two_views_one_four",
  "two_views_two_three",
  "two_views_two_four",
  "two_views_three_four"
)
  

for ( i in 1:6){  # columns
  
  for ( j in 1:6 ){ # rows
    
        table[j,i] = mean ( matrices[[i]] [ get( views[j] ) ] )
                           
    }
} 

# Transform to data frame and assign col- and row names
table = as.data.frame(table)
colnames(table) = methods
rownames(table) = views

# Print object as table        
table %>%   
  kbl(caption = "MPsV: Size of views and Signal / Noise differentiation for Nviews = 2", digits = 2, row.names = TRUE) %>%
  kable_classic( full_width = T, html_font = "Times New Roman", position = "left")

```


### True Positive Rate (TPR)

```{r, echo = F}

# Create 100 x 80 matrices for each method

# Create an object with the names of objects containing the results of each method
methods = c("meta_mean", "meta_cv", "meta_pmm", "meta_forest", "CCA", "CDA")

# Create two list objects, one to collect matrices and one to collect means and SDs
matrices = list()
Means_SDs = list()

# Create a second index j to update with each iteration
j = 1

for (i in methods) {
  
  # Create and save accuracy scores as matrix where each condition appears as a column
  matrices[[j]] = matrix( get( paste0(i) )$TPR, ncol = 80)
  
  # Use matrices to create a table with mean and SD for each method
  Means_SDs[[j]] = data.frame( mean = apply( matrices[[j]] , 2, mean),
                               sd = apply( matrices[[j]] , 2, sd))
  
  # Assign names
  names(matrices) [[j]] = paste0("mat_",i)
  
  names(Means_SDs) [[j]] = paste0("TA_table_", i)
  
  # Update second index j
  j = j + 1 
  
}
  
```


#### Number of views = 1

```{r, echo = F}

# Create a matrix to collect values for the later table
table = matrix(0, nrow = 4, ncol = 6)

# object containing objects with indeces for each level of missingness in views
views = c( "one_view_one", 
           "one_view_two", 
           "one_view_three", 
           "one_view_four" )

for ( i in 1:6){  # columns
  
  for ( j in 1:4 ){ # rows
    
        table[j,i] = mean ( matrices[[i]] [ get( views[j] ) ] )
                           
    }
} 

# Transform to data frame and assign col- and row names
table = as.data.frame(table)
colnames(table) = methods
rownames(table) = c(1:4)

# Print object as table        
table %>%   
  kbl(caption = "TPR: Size of views and Signal / Noise differentiation for Nviews = 1", digits = 2, row.names = TRUE) %>%
  kable_classic( full_width = T, html_font = "Times New Roman", position = "left")

```


#### Number of views = 2


```{r, echo = F}

# Create a matrix to collect values for the later table
table = matrix(0, nrow = 6, ncol = 6)

# object containing objects with indeces for each level of missingness in views
views = c(
  "two_views_one_two",
  "two_views_one_three",
  "two_views_one_four",
  "two_views_two_three",
  "two_views_two_four",
  "two_views_three_four"
)
  

for ( i in 1:6){  # columns
  
  for ( j in 1:6 ){ # rows
    
        table[j,i] = mean ( matrices[[i]] [ get( views[j] ) ] )
                           
    }
} 

# Transform to data frame and assign col- and row names
table = as.data.frame(table)
colnames(table) = methods
rownames(table) = views

# Print object as table        
table %>%   
  kbl(caption = "TPR: Size of views and Signal / Noise differentiation for Nviews = 2", digits = 2, row.names = TRUE) %>%
  kable_classic( full_width = T, html_font = "Times New Roman", position = "left")

```


### False positive rate (FPR) 

```{r, echo = F}

# Create 100 x 80 matrices for each method

# Create an object with the names of objects containing the results of each method
methods = c("meta_mean", "meta_cv", "meta_pmm", "meta_forest", "CCA", "CDA")

# Create two list objects, one to collect matrices and one to collect means and SDs
matrices = list()
Means_SDs = list()

# Create a second index j to update with each iteration
j = 1

for (i in methods) {
  
  # Create and save accuracy scores as matrix where each condition appears as a column
  matrices[[j]] = matrix( get( paste0(i) )$FPR, ncol = 80)
  
  # Use matrices to create a table with mean and SD for each method
  Means_SDs[[j]] = data.frame( mean = apply( matrices[[j]] , 2, mean),
                               sd = apply( matrices[[j]] , 2, sd))
  
  # Assign names
  names(matrices) [[j]] = paste0("mat_",i)
  
  names(Means_SDs) [[j]] = paste0("TA_table_", i)
  
  # Update second index j
  j = j + 1 
  
}
  
```


#### Number of views = 1

```{r, echo = F}

# Create a matrix to collect values for the later table
table = matrix(0, nrow = 4, ncol = 6)

# object containing objects with indeces for each level of missingness in views
views = c( "one_view_one", 
           "one_view_two", 
           "one_view_three", 
           "one_view_four" )

for ( i in 1:6){  # columns
  
  for ( j in 1:4 ){ # rows
    
        table[j,i] = mean ( matrices[[i]] [ get( views[j] ) ] )
                           
    }
} 

# Transform to data frame and assign col- and row names
table = as.data.frame(table)
colnames(table) = methods
rownames(table) = c(1:4)

# Print object as table        
table %>%   
  kbl(caption = "FPR: Size of views and Signal / Noise differentiation for Nviews = 1", digits = 2, row.names = TRUE) %>%
  kable_classic( full_width = T, html_font = "Times New Roman", position = "left")

```


#### Number of views = 2


```{r, echo = F}

# Create a matrix to collect values for the later table
table = matrix(0, nrow = 6, ncol = 6)

# object containing objects with indeces for each level of missingness in views
views = c(
  "two_views_one_two",
  "two_views_one_three",
  "two_views_one_four",
  "two_views_two_three",
  "two_views_two_four",
  "two_views_three_four"
)
  

for ( i in 1:6){  # columns
  
  for ( j in 1:6 ){ # rows
    
        table[j,i] = mean ( matrices[[i]] [ get( views[j] ) ] )
                           
    }
} 

# Transform to data frame and assign col- and row names
table = as.data.frame(table)
colnames(table) = methods
rownames(table) = views

# Print object as table        
table %>%   
  kbl(caption = "FPR: Size of views and Signal / Noise differentiation for Nviews = 2", digits = 2, row.names = TRUE) %>%
  kable_classic( full_width = T, html_font = "Times New Roman", position = "left")

```


### False discovery rate (FDR)

```{r, echo = F}

# Create 100 x 80 matrices for each method

# Create an object with the names of objects containing the results of each method
methods = c("meta_mean", "meta_cv", "meta_pmm", "meta_forest", "CCA", "CDA")

# Create two list objects, one to collect matrices and one to collect means and SDs
matrices = list()
Means_SDs = list()

# Create a second index j to update with each iteration
j = 1

for (i in methods) {
  
  # Create and save accuracy scores as matrix where each condition appears as a column
  matrices[[j]] = matrix( get( paste0(i) )$FDR, ncol = 80)
  
  # Use matrices to create a table with mean and SD for each method
  Means_SDs[[j]] = data.frame( mean = apply( matrices[[j]] , 2, mean),
                               sd = apply( matrices[[j]] , 2, sd))
  
  # Assign names
  names(matrices) [[j]] = paste0("mat_",i)
  
  names(Means_SDs) [[j]] = paste0("TA_table_", i)
  
  # Update second index j
  j = j + 1 
  
}
  
```


#### Number of views = 1

```{r, echo = F}

# Create a matrix to collect values for the later table
table = matrix(0, nrow = 4, ncol = 6)

# object containing objects with indeces for each level of missingness in views
views = c( "one_view_one", 
           "one_view_two", 
           "one_view_three", 
           "one_view_four" )

for ( i in 1:6){  # columns
  
  for ( j in 1:4 ){ # rows
    
        table[j,i] = mean ( matrices[[i]] [ get( views[j] ) ] )
                           
    }
} 

# Transform to data frame and assign col- and row names
table = as.data.frame(table)
colnames(table) = methods
rownames(table) = c(1:4)

# Print object as table        
table %>%   
  kbl(caption = "FDR: Size of views and Signal / Noise differentiation for Nviews = 1", digits = 2, row.names = TRUE) %>%
  kable_classic( full_width = T, html_font = "Times New Roman", position = "left")

```


#### Number of views = 2


```{r, echo = F}

# Create a matrix to collect values for the later table
table = matrix(0, nrow = 6, ncol = 6)

# object containing objects with indeces for each level of missingness in views
views = c(
  "two_views_one_two",
  "two_views_one_three",
  "two_views_one_four",
  "two_views_two_three",
  "two_views_two_four",
  "two_views_three_four"
)
  

for ( i in 1:6){  # columns
  
  for ( j in 1:6 ){ # rows
    
        table[j,i] = mean ( matrices[[i]] [ get( views[j] ) ] )
                           
    }
} 

# Transform to data frame and assign col- and row names
table = as.data.frame(table)
colnames(table) = methods
rownames(table) = views

# Print object as table        
table %>%   
  kbl(caption = "FDR: Size of views and Signal / Noise differentiation for Nviews = 2", digits = 2, row.names = TRUE) %>%
  kable_classic( full_width = T, html_font = "Times New Roman", position = "left")

```

